### 2013-03-28 doc/sosp13/overview.tex
po

\item[Communication layer.] The main goal of our communication layer is to
aggregate small messages into large ones, invisible to the application
programmer. Its interface is based on active messages~\cite{vonEicken92}.
Since aggregation and deaggregation of messages needs to be very efficient, we
made it highly concurrent with careful use of lock-free synchronization
operations.

>>>>

\item[Communication layer.] The main goal of our communication layer is to
aggregate small messages into large ones.  This process is invisible to the application
programmer. Its interface is based on active messages~\cite{vonEicken92}.
Since aggregation and deaggregation of messages needs to be very efficient, we perform the process in parallel and carefully use lock-free synchronization
operations.
